### 2025-05-30 thesis_julio/Chapter1/chapter1.tex
30may

Supposing a beam of incoming particles with a value L that is associated with the number of particles passing down the line per unit of time and per unit of area $dN = L d\sigma $ is the number of particles per unit time passing trough area $d\sigma$ and hence also the number per unit of time scattered into solid the solid angle $d\Omega$

\begin{equation}
dN = L d\sigma = LD(\theta) d\Omega 
\end{equation}

This could be seeing as the one who controls the number of particles going through the detector also determined the solid angle.

@@

The performance of a collider is determined by the beam energy and the luminosity, theluminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions\cite{Lum}

\begin{equation}
N = L \cdot \sigma_{p} 
\end{equation}

In which N is the number of events per second, the $\simga_{p}$ is the cross section and L the instantanious luminosity luminosity. The unity of L is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.

To compute the luminosity of two there is a few things that need to be taken in consideration. First the density distribution of each beam in the transverse and longitudinal plane, with the. two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$. The figure (1.x) shows a  In principle each of the distributions is different the overlap integral can be written as follow:

@@

In principle each of the distributions is different and we can write the overlap integral as follow:
%$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }

\begin{equation}
 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
\end{equation}

With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions, this is assuming the velocity on the beams is $v1 = -v2$ and the densities are uncorrelated in all planes the overlap integral takes the form of: \cite{Lumvdm}

>>>>

Supposing a beam of incoming particles with a value F that is associated with the number of particles passing down the line per unit of time and per unit of area $dN = F d\sigma $ is the number of particles per unit time passing trough area $d\sigma$ and hence also the number per unit of time scattered into solid the solid angle $d\Omega$

\begin{equation}
dN = F d\sigma = fD(\theta) d\Omega 
\end{equation}

This is a classical description of scattering and could be seen as the one who controls the number of particles going through the detector also determined the solid angle. Here we have the incident flux F and a cross sectional area and are a way to interpret collision rates in modern particle accelerators since in high energy physics this structure is similar with a quantity called luminosity L with Its own cross section $\sigma$.

Even when the dynamics are different for the quantum field theory case, the general principle remains the same, when we have a  higher the cross section we obtain a higher luminosity and Its more likely to observer determined events.

@@

The performance of a collider is determined by the beam energy and the luminosity, the luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions\cite{Lum}

\begin{equation}
R = L \cdot \sigma_{p} 
\end{equation}

In which R is the number of events per second or rate, the $\sigma_{p}$ is the cross section which in the quantum case is a probability of interaction which can be obtained from the standar model of particle physics and L the instantanious luminosity. The unity of L is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.

To compute the luminosity of two there is a few things that need to be taken in consideration. First the density distribution of each beam in the transverse and longitudinal plane, with the. two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$. The figure (1.x) shows two beams colliding which depends on a variety of factors:

@@

Following this we can write the integral for luminosity, in principle each of the distributions is different and we can write the overlap integral as follow:
%$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }

\begin{equation}
 L = 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
\end{equation}

With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.  \cite{Lumvdm}

### 2025-05-30 thesis_julio/Chapter2/chapter2.tex
30may

The first step to the reconstruction process is referred to as local reconstruction. It consist of the clustering of zero-suppressed signals above specific thresholds in pixel and strip channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor.  \cite{cluster2}

@@

The pixel detector has a total of 1856 modules (1184 on the BPIX and 672 on FPIX) in this analysis for the pcc vdm calibration on 2024 for the fill 9639, a total of 1616 modules were removed for a total of 240 modules with 193 in the BPIX part of the detector and the other ones on the FPIX part.

>>>>

The first step to the reconstruction process is referred to as local reconstruction. It consist of the clustering of zero-suppressed signals above specific thresholds in pixel and strip channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor. The sensor has a total of 100 x 150 $\mu m^{2}$ pixels with the u axis oriented parallel to the shorter pixel edge and for the strip sensors the u-axis is perpendicular to the central strip in the sensors.   \cite{cluster2}

During the data acquisition on the pixel detector a zero suppresion is performed in the readout chips of the sensors, with adjustable threshold for each pixel. This pixels read-out threshold is set to a single pixel equivalent to a charge of 3200 electrons. Offline, pixel clusters are formed from adjacent pixels. Each of these clusters must have a minimum charge of at least 4000 electrons. Misscalibration of residual charges caused by the pixel to pixel differences of the charge injection capacitors, which are used to calibrate pixel gain are extracted from laboratory measurements and the Monter Carlo simulator.

There are two algorithms for determine the positions of the pixel clusters, a fast one that is called first pass hit reconstruction and is used during the track seeding and pattern recognition and the second algorithm called template based hit reconstruction which is more precise and is based on cluster shapes and used in the final track fit.

@@

On summary, in the analysis for the PCC vdm calibration on 2024 for the fill 9639, a total of 1616 modules were removed for a total of 240 good modules with 193 in the BPIX part of the detector and the other ones on the FPIX part.

### 2025-05-30 thesis_julio/Chapter3/chapter3.tex
30may

 \begin{equation}
N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy   = N_{1} N_{2} f (\int \rho_{1}(x)\rho_{2}(x + \Delta x) dx) (\int rho_{1}(y) \rho_{2}(y + \Delta y) dy)
\end{equation}

@@

\begin{equation}
N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
\end{equation}

@@

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
\end{equation}

@@

\begin{equation}
\sigma_{vis} = \frac{2 \pi \Sigma_{x} Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
\end{equation}

@@

\begin{table} [H]
\begin{center}
\caption{Different Scans}
\begin{tabular}{|c c c|} 
 \hline
 Scan & Mean & std  \\ [0.5ex] 
 \hline\hline
 SS1 &  & 1715883481  \\ 
 \hline
 SS2 &  & 1715902484  \\
 \hline
 SS3 &  & 1715919463 \\
 \hline
 SS6 &  & 1715943343  \\
 \hline
 SS5 &  & 1715987602  \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained

@@

@@

@@

>>>>

 \begin{equation}
N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy   = N_{1} N_{2} f (\int \rho_{1}(x)\rho_{2}(x + \Delta x) dx) (\int \rho_{1}(y) \rho_{2}(y + \Delta y) dy)
\end{equation}

@@

\begin{equation}
N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
\end{equation}

@@

\begin{equation}
L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
\end{equation}

@@

\begin{equation}
\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
\end{equation}

@@

\begin{table} [H]
\begin{center}
\caption{Different Scans}
\begin{tabular}{|c c c|} 
 \hline
 Scan & Mean & std  \\ [0.5ex] 
 \hline\hline
 SS1 &  & 1715883481  \\ 
 \hline
 SS2 &  & 1715902484  \\
 \hline
 SS3 &  & 1715919463 \\
 \hline
 SS4 &  & 1715943343  \\
 \hline
 SS5 &  & 1715987602  \\ [1.0ex]
 \hline
\end{tabular}
\end{center}
\end{table}

This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained and was $ss_background$ = 0.0251 +-0.0018 in the following picture we can see the

@@

A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdm framework.

\begin{itemize}
  \item \textbf{Background} The rates substracted on the SS periods and is associated with the luminometer itself see section (3.x) for more.
  \item \textbf {Ghost Satellite} This correction have to be with the charge that comes from the non colliding bunches, which are called ghost and those who are leaking from the main radio frequency bucket into another bucket which are called satellite. This currents have an effect on the $\sigma_{visible}$ measure because of the contribution on the charges, this charges are substracted from the beam currents.  \cite{ghost}
  \item \textbf{BeamBeam} This are deflections that happen between bunch crossings, accounting for the electrical repulsion of the beams which increases the lateral separation.   \cite{beambeam}
  \item \textbf{Dynamic beta} This correction accounts for any changes in the proton density distributions of the bunches due to the single particle interaction, resulting into a non linear change during separation steps in transverse bunch profiles and can be described as the effective changes of a called $\beta$ value. \cite{LHClum}
\end{itemize}

@@

For the main calibration we used the QG fit this fit uses the parameter $\sigma$, the peak and a q values as the parameters. This fit is given by the following equation:

\begin{equation}
f_{qg}(x,y) = \frac{V}{C(q) \sigma_{x} \sigma_{y}\sqrt{1-\chi^{2}}} e_{q}(\frac{\ r^{2}}{(4-2q)}) 
\end{equation}

with $e_{q}$ being a function of x defined as:

\begin{equation}
e_{q}(x) = (1+(1-q)x)^{\frac{1}{1-q}}
\end{equation}

and $c(q)$ having two different values depending on the value of the q, for q < 1:

\begin{equation}
c(q) = \frac{4-2q}{1-q} \pi \frac{\Gamma (\frac{2-q}{1-q})}{\Gamma (\frac{2-q}{1-q} + 1)}
\end{equation}

and for the other cases:

\begin{equation}
c(q) = \frac{4-2q}{q-1} \pi \frac{\Gamma (\frac{1}{q-1} - 1)}{\Gamma (\frac{1}{q-1})}
\end{equation}

@@

The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained was the peak:
